\begin{theorem}[BS-7.2.7]
    Monotone functions on $[a, b]$ are integrable.
\end{theorem}

\begin{proof}
    We show only for increasing. Let $f: [a, b] \to \R$ be monotone increasing. If $f$ constant, then it is a step function and we are done.

    Otherwise, $f(b) - f(a) > 0$. Let $\epsilon > 0$ and $q \in \N$ such that $h \defeq \frac{f(b)-f(a)}{q} < \frac{\epsilon}{b-a}$, effectively subdividing the $y$-axis into $q$ equal-sized parts. Then, let \[
    y_i \defeq f(a) + i h, \quad 0 \leq i \leq q,    
    \]
    and take $$A_k \defeq f^{-1}([y_{k+1}, y_k)) = \begin{cases}
        \varnothing\\
        \{x\}\\
        I_i
    \end{cases}.$$
    We disregard each $A_k : A_k = \varnothing$, and adjoin the isolated points $\{x\}$ to the $I_i$'s, and hence have a partition $\cup_k A_k = [a, b]$. Letting $\alpha(x) = y_{k-1}$ and $\omega(x) = y_k$ for $x \in A_k$, then $\alpha(x) \leq f(x) \leq \omega(x) \forall x \in [a, b]$ (effectively, we are created a "series of squeezes"). Then, \[
    \int_{a}^b \omega(x) - \alpha(x) \dd{x} = \sum_{k=1}^q (y_k - y_{k-1})(x_k-x_{k-1}) = h (b-a) < \epsilon,
    \]
    and the proof is completed by applying the squeeze theorem.
\end{proof}

\begin{theorem}[Additivity; BS-7.2.8]
    Let $f : [a, b] \to \R$ and $a < c < b$. Then,  $f \in \mathcal{R}[a, b]$ $\iff f \in \mathcal{R}[a, c]$ and $f \in \mathcal{R}[c, b]$. Moreover, $\int_a^b f(x) \dd{x} = \int_a^c f(x) \dd{x} + \int_c^b f(x) \dd{x}$.
\end{theorem}

\begin{proof}
    See book. Remark that this holds for finite summations of integrals as such by induction.
\end{proof}

\subsection{Fundamental Theorem of Calculus}

\begin{definition}
    Call $F(x)$ a \emph{primitive} of $f(x)$ if $F$ differentiable and $F'(x) = f(x)$.
\end{definition}

\begin{theorem}[Fundamental Theorem of Calculus]
    Let $F, f : [a, b] \to \R$ and $E \subseteq [a, b]$ a finite set \st
    \begin{enumerate}
        \item $F$ continuous on $[a, b]$
        \item $F'(x) = f(x) \forall x \in [a, b]\setminus E$; ie they agree for all but finitely many points
        \item $f \in \mathcal{R}[a, b]$
    \end{enumerate}
    Then, $\int_a^b f(x) = F(b) - F(a)$.
\end{theorem}
\begin{proof}(Sketch)
    Remark first that it suffices to prove for $E \defeq \{a, b\}$; using additivity, we can subdivide any other such $E$ into such subsets of $1$ or $2$ elements.

    Fix $\epsilon > 0$ and take $\delta > 0$ such that for any $\dot{P}$ of $[a, b]$ \st $\diam \dot{P} < \delta$, $\abs{S(f, \dot{P}) - \int_a^b f(x)} < \epsilon$. Applying the mean value theorem to $F$ on each $[x_{i-1}, x_i]$ of $\dot{P}$:
    \begin{align*}
        F(x_i) - F(x_{i-1}) &= F'(u_i)(x_i - x_{i-1}), \quad u_i \in [x_{i-1}, x_i] \\
        &= f(u_i)(x_i-x_{i-1})
    \end{align*}
    Hence, summing over each of these, \begin{align*}
        F(x_1) - \cancelto{F(a)}{F(x_0)} + F(x_2) - F(x_1) + \cdots + \cancelto{F(b)}{F(x_{n})} - F(x_{n-1}) = f(u_1)(x_1 - a) + \cdots + f(u_n)(x_n - x_{n-1})\\
        \implies F(b) - F(a) = \sum_{i=1}^n f(u_i) (x_i - x_{i+1}) =: S(f, \dot{P_1})
    \end{align*}
    by construction, $\diam(\dot{P_1}) < \delta$ since the only change we have made from $\dot{P}$ is the tags, hence $\abs{S(f, \dot{P_1}) - \int_a^b f(x)} < \epsilon$. Thus, \begin{align*}
        \abs{S(f, \dot{P_1}) - \int_a^b f(x)} = \abs{F(b) - F(a) - \int_a^b f(x)} < \epsilon\\
        \implies F(b) - F(a) = \int_a^b f(x) \quad \text{as }\epsilon \to 0.
    \end{align*}
\end{proof}